Reliable feature point matching

### 2013-08-06 text/thesis.tex
Added section about near duplicate detection

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognitize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and fails to
produce a panorama as a result.

@@

When we are performing panorama alignment and recognition with feature 
points, oth recognition and alignment of the source images is

>>>>

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognitize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

This example illustrates how an improved matching algorithm can be 
applied to panorama recognition and alignment to allow for panoramas 
created with images that have little overlap.
% Maybe find example of images with identical features that would be 
% hard to match?

\subsection{Near Duplicate Detection}
Both with regards to corporate intellectual property as well as consumer 
photo albums, being able to automatically find near duplicates of images 
provides useful across several scenarios. A company might be interested 
in finding images that are derived from their intellectual property, 
while consumers taking vacation photos might be interested in grouping 
duplicate images to allow for easier photo organization.

Local features are often used to group similar images, either by looking
at a histogram of descriptors \cite{wu2009bundling} or by looking at how
well feature points match between images \cite{zhao2009scale},
\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
finding near duplicates means that we will be matching image pairs that 
might or might not contain any actual matches. In this case we would 
benefit from a reliable matching algorithm that minimizes false 
positives, which is a characteristic of both \emph{MM} and \emph{MMC}.

The PhotoCluster method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
California-nd dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. PhotoCluster works by grouping images in several steps using 
first image metadata and global features to obtain a set of proposed 
clusters. Then local features are used to find the best matching images 
in these proposed clusters yielding the final groups of near duplicate 
images. To show the viability of \emph{MMC} in the application of near 
duplicated detection, we modify the PhotoCluster method to use 
\emph{MMC} for matching images instead of \emph{Ratio} which was 
previously used. Due to the time consumption of \emph{MMC}, all images 
where resized to to 10\% before being compared. Outside of that, the 
experiments were performed exactly as documented in 
\cite{vas2013cluster}.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection at 10\% scale}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{2}{r}}
\hline
    Method: & Ratio & MMC   \\
	\noalign{\smallskip}
	%
    F1 score: & 0.4654 & 0.5459 \\
	\hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:nnd} where
\emph{MMC} improves performance by 8.05\% over the original framework 
using \emph{Ratio} to match images.

@@
